Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-28 GWLDCII.tex
added a note about the conversation we were having

Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.  Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$. (This just replicates the behavior of the algorithm, which removes each propagator once it contibutes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.  Again obtain $V'$ from $V$ by removing all propagators assigned so far. \sanote{rewrote, do we like this?}\note{Sian: rewrote some more. We need to be a bit careful with ``contributes'' because $p$ is assigned, not contributed, by the algorithm: vertices are contributed, propagators contribute.}

>>>>

 \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same or actually the function}

Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.  Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$. (This just replicates the behavior of the algorithm, which removes each propagator once it contibutes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.  Again obtain $V'$ from $V$ by removing all propagators assigned so far.
